### 2016-06-05 thesis_paper/source.tex
thesis

\section{Network of queries organization}

@@

@@

As you can see, speedup bumps up to almost 30 with 10000 atoms. Once the overhead on memory transfer is covered by computation speedup, it keeps growing. It is important to pay attention to the growth of speedup over growth of workload. It is not that significant, because even though CPUs are much slower, they still use smart caching and internal multi-core processing, which is pretty fast, too, while GPU does pretty straightforward multicore processing, which is the main reason it stagnates.

@@

@@

\begin{figure}
 \centerline{\includegraphics[width=0.5\columnwidth]{images/chart_max}}
 \caption{Speedup for larger number of atoms}
 \label{fg:chart_max}
\end{figure}

@@

\chapter{Conclusions and Future Work}\label{sc:conclusion}
The ultimate goal of this work was to get an improved version of Push-based system for molecular simulation data analysis. As you could see from result on charts (Figure \ref{fg:chart_1000}, \ref{fg:chart_max}), the proposed improved version of the system could save a lot of time for scientists which is up to 60-70 times less of time. The results have been gathered with a single snapshot of the framework tracked in control version system which can be improved with means of data converter module and dynamic grid dimensions computation module. In the future, this system has all potentials to be expanded into a distributed system, where frames could be aggregated by nodes and processed in parallel.\\

>>>>

\section{Queries organization}

@@

\begin{table}[h!]
	\renewcommand*{\arraystretch}{1.5}
	\tabcolsep=0.12cm
  \centering
  \begin{tabular}{| c | c | c | c | c | c |}
   \hline

$Duration$ & $Grid Size$ & $Block Size$ & $DSMem*$ & $Size$ & $Throughput$ \\ \hline 
$1.1830us$ & $-$ & $-$ & $-$ & $4B$ & $3.3812MB/s$ \\ \hline 
$6.0470us$ & $-$ & $-$ & $-$ & $36.000KB$ & $5.9534GB/s$ \\ \hline 
$1.0240us$ & $-$ & $-$ & $-$ & $36B$ & $35.156MB/s$ \\ \hline 
$1.2160us$ & $-$ & $-$ & $-$ & $1.4080KB$ & $1.1579GB/s$ \\ \hline 
$234.16us$ & $(1,1,1)$ & $(1024,1,1)$ & $40.960KB$ & $-$ & $-$ \\ \hline 
$3.1640ms$ & $(1,1,1)$ & $(1024,1,1)$ & $38.272KB$ & $-$ & $-$ \\ \hline 
$2.5280us$ & $-$ & $-$ & $-$ & $36B$ & $14.241MB/s$ \\ \hline 
$2.4960us$ & $-$ & $-$ & $-$ & $1.4080KB$ & $564.10MB/s$ \\
	\hline

  \end{tabular}
    \caption{Memory profiling results for 1000 atoms}
    	  \label{tb:gpumem1000}
\end{table}

@@

\vspace{1cm}
\begin{table}[h!]
	\renewcommand*{\arraystretch}{1.5}
	\tabcolsep=0.12cm
  \centering
  \begin{tabular}{| c | c | c | c | c | c |}
   \hline
	Device & Context & Stream & Kernel & Warps Launched & Shared Load \\ \hline
	GRID K520 (0) & 1 & 13 & ${gpu\_one\_body\_function}$ & 320 & 20 \\ \hline
	GRID K520 (0) & 1 & 14 & ${gpu\_two\_body\_function}$ & 320 & 5,181,545 \\ \hline

  \end{tabular}
    \caption{GPU profiling results for 10,000 atoms}
    	  \label{tb:gpuprofile10000}
\end{table}

\begin{table}[h!]
	\renewcommand*{\arraystretch}{1.5}
	\tabcolsep=0.12cm
  \centering
  \begin{tabular}{| c | c | c | c | c | c |}
   \hline

$Duration $ & $ Grid Size $ & $ Block Size $ & $ DSMem* $ & $ Size $ & $ Throughput  $ \\ \hline
$1.1840us $ & $ - $ & $ - $ & $ - $ & $ 4B $ & $ 3.3784MB/s  $ \\ \hline
$42.470us $ & $ - $ & $ - $ & $ - $ & $ 360.00KB $ & $ 8.4766GB/s  $ \\ \hline
$1.0240us $ & $ - $ & $ - $ & $ - $ & $ 36B $ & $ 35.156MB/s  $ \\ \hline
$1.2480us $ & $ - $ & $ - $ & $ - $ & $ 1.4080KB $ & $ 1.1282GB/s  $ \\ \hline
$456.86us $ & $ (10,1,1) $ & $ (1024,1,1) $ & $ 40.960KB $ & $ - $ & $ -  $ \\ \hline
$59.627ms $ & $ (10,1,1) $ & $ (1024,1,1) $ & $ 38.272KB $ & $ - $ & $ -  $ \\ \hline
$2.7520us $ & $ - $ & $ - $ & $ - $ & $ 36B $ & $ 13.081MB/s  $ \\ \hline
$2.7850us $ & $ - $ & $ - $ & $ - $ & $ 1.4080KB $ & $ 505.57MB/s$ \\

	\hline

  \end{tabular}
    \caption{Memory profiling results for 10,000 atoms}
    	  \label{tb:gpumem10000}
\end{table}

As you can see, speedup bumps up to almost 30 with 10000 atoms. Once the overhead on memory transfer is covered by computation speedup, it keeps growing. It is important to pay attention to the growth of speedup over growth of workload. It is not that significant, because even though CPUs are much slower, they still use smart caching and internal multi-core processing, which is pretty fast, too, while GPU does pretty straightforward multicore processing, which is the main reason it stagnates.
Result of another profiling on Table \ref{tb:gpuprofile100000} changed significantly in terms of warps launched, which is reasonable, and shared memory. It is also noticeable that growth of shared memory loading instructions is non-linear which you can observe in the results for 100K atoms.

@@

\begin{table}[h!]
	\renewcommand*{\arraystretch}{1.5}
	\tabcolsep=0.12cm
  \centering
  \begin{tabular}{| c | c | c | c | c | c |}
   \hline

 $Duration $ & $ Grid Size $ & $ Block Size $ & $ DSMem* $ & $ Size $ & $ Throughput $ \\ \hline 
 $1.1840us $ & $ - $ & $ - $ & $ - $ & $ 4B $ & $ 3.3784MB/s $ \\ \hline 
 $729.81us $ & $ - $ & $ - $ & $ - $ & $ 3.6000MB $ & $ 4.9328GB/s $ \\ \hline 
 $992ns $ & $ - $ & $ - $ & $ - $ & $ 36B $ & $ 36.290MB/s $ \\ \hline 
 $1.2160us $ & $ - $ & $ - $ & $ - $ & $ 1.4080KB $ & $ 1.1579GB/s $ \\ \hline 
 $3.0014ms $ & $ (98,1,1) $ & $ (1024,1,1) $ & $ 40.960KB $ & $ - $ & $ - $ \\ \hline 
 $3.86896s $ & $ (98,1,1) $ & $ (1024,1,1) $ & $ 38.272KB $ & $ - $ & $ - $ \\ \hline 
 $3.0720us $ & $ - $ & $ - $ & $ - $ & $ 36B $ & $ 11.719MB/s $ \\ \hline 
 $2.9760us $ & $ - $ & $ - $ & $ - $ & $ 1.4080KB $ & $ 473.12MB/s $ \\ \hline

	\hline
  \end{tabular}
    \caption{Memory profiling results for 100,000 atoms}
    	  \label{tb:gpumem100000}
\end{table}

@@

\begin{table}[h!]
	\renewcommand*{\arraystretch}{1.5}
	\tabcolsep=0.12cm
  \centering
  \begin{tabular}{| c | c | c | c | c | c |}
   \hline
	Device & Context & Stream & Kernel & Warps Launched & Shared Load \\ \hline
	GRID K520 (0) & 1 & 13 & ${gpu\_one\_body\_function}$ & 3136 & 196 \\ \hline
	GRID K520 (0) & 1 & 14 & ${gpu\_two\_body\_function}$ & 3136 & 473,692,099 \\ \hline

  \end{tabular}
    \caption{GPU profiling results for 100,000 atoms}
    	  \label{tb:gpuprofile100000}
\end{table}

Finally, for 100,000 atoms the warps launched for execution seems to be growing reasonable along with number of atoms (Table \ref{tb:gpuprofile100000}), while on the other hand usage of shared load for SDH computation is extremely high.

\subsection{Overall performance}

@@

\begin{figure}
 \centerline{\includegraphics[width=0.7\columnwidth]{images/chart_max}}
 \caption{Speedup for larger number of atoms}
 \label{fg:chart_max}
\end{figure}

\chapter{Conclusions and Future Work}\label{sc:conclusion}
The ultimate goal of this work was to get an improved version of Push-based system for molecular simulation data analysis. As you could see from result on charts, the proposed improved version of the system could save a lot of time for scientists which is up to 60-70 times less of time. The results have been gathered with a single snapshot of the framework tracked in control version system which can be improved with means of data converter module and dynamic grid dimensions computation module. In the future, this system has all potentials to be expanded into a distributed system, where frames could be aggregated by nodes and processed in parallel.\\
